From OpenACC to OpenMP 4: \\ Toward Automatic Translation

### 2016-04-29 paper.tex
Wrote conclusion

Our tool is a prototype, and our translation algorithm supports only a few
commonly used OpenACC directives.  Some areas for improvement are obvious.  The
algorithm needs to be expanded to include the entire OpenACC specification,
including asynchronous kernel launches, unstructured data lifetimes, and
OpenACC API calls.  Our tool works only on C, while OpenACC and OpenMP both
support C++ and Fortran.  While the EPCC benchmarks were useful for evaluating
our prototype, we need to test its effectiveness on larger code bases (i.e.,
application codes), ideally by working with other XSEDE collaborators.

@@

%\section{Conclusion}

@@

>>>>

Our tool is a prototype, and our translation algorithm supports only the most
commonly used OpenACC directives.  Some areas for improvement are obvious.  The
algorithm needs to be expanded to include the entire OpenACC specification,
including asynchronous kernel launches, unstructured data lifetimes, and
OpenACC API calls.  Our tool works only on C, while OpenACC and OpenMP both
support C++ and Fortran.  While the EPCC benchmarks were useful for evaluating
our prototype, we need to test its effectiveness on larger code bases (i.e.,
application codes), ideally by working with other XSEDE collaborators.

@@

\section{Conclusion}

We have described an algorithm (\S\ref{sec:algorithm}) and a prototype tool
that converts a subset of OpenACC (Figure~\ref{fig:grammar}) to OpenMP~4.  The
translation algorithm was designed to be simple and predicatble, since it will
necessarily be used in conjunction with manual restructuring and performance
tuning.  We evaluated our tool by converting the EPCC Level~1 OpenACC
benchmarks from OpenACC compiled by PGI C/C++ to OpenMP~4 compiled by Clang.
Both targeted an NVIDIA GPU (Tesla~K40).  To keep the translation process
transparent, the programmer was required to manually convert OpenACC
\emph{kernels} loops, although the tool was able to automatically translate the
remaining 67 of 70 OpenACC directives

@@

\newpage
